Unit 6 - Clustering: Assignment 3 - Stocks
============================================
Loading and Pre-Processing
====================================
```{r}
stocks = read.csv("StocksCluster.csv")
str(stocks)
summary(stocks)
```
Splitting the Data
=====================================
```{r}
suppressWarnings(library(caTools))
set.seed(144)
spl = sample.split(stocks$PositiveDec, SplitRatio = 0.7)
stocksTrain = subset(stocks, spl == TRUE)
stocksTest = subset(stocks, spl == FALSE)
```
Baseline Model
=====================================
```{r}
basetable = table(stocksTest$PositiveDec)
```
**Accuracy:** `r max(c(basetable[1],basetable[2]))/sum(basetable)`

Logistic Regression Model
========================================
```{r}
stocksModel = glm(PositiveDec ~ ., data=stocksTrain, family=binomial)
summary(stocksModel)
```
Predictions on the Training Set
----------------------------------------
```{r}
pred = predict(stocksModel, newdata=stocksTrain, type="response")
predtable = table(stocksTrain$PositiveDec, pred >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
Predictions on the Test Set
----------------------------------------
```{r}
pred = predict(stocksModel, newdata=stocksTest, type="response")
predtable = table(stocksTest$PositiveDec, pred >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
Clustering
=================================
First we removed the dependant variables from our training and testing data
```{r}
limitedTrain = stocksTrain
limitedTrain$PositiveDec = NULL
limitedTest = stocksTest
limitedTest$PositiveDec = NULL
```
Pre-Processing for Clustering
--------------------------------------
```{r}
suppressWarnings(library(caret))
preproc = preProcess(limitedTrain)
normTrain = predict(preproc, limitedTrain)
normTest = predict(preproc, limitedTest)
summary(normTrain)
summary(normTest)
```
Notice that the means of normTrain are all 0.000, while normTest are not. Since normTest was constructed from the pre processing of normTrain, this explains why they are different. The distribution of the variables are different between the testing and training set.
K-Means Clustering
=======================================
```{r}
k=3
set.seed(144)
KMC = kmeans(normTrain, centers=k)
KMCGroups = KMC$cluster
KMCCluster = split(normTrain, KMCGroups)
nrow(KMCCluster[[1]])
nrow(KMCCluster[[2]])
nrow(KMCCluster[[3]])
```
Using flexclust to Test Prediction Accuracy
===========================================
```{r}
suppressWarnings(library(flexclust))
km.kcca = as.kcca(KMC, normTrain)
clusterTrain = predict(km.kcca)
clusterTest = predict(km.kcca, newdata=normTest)
stocksTrain1 = subset(stocksTrain, clusterTrain==1)
stocksTrain2 = subset(stocksTrain, clusterTrain==2)
stocksTrain3 = subset(stocksTrain, clusterTrain==3)
stocksTest1 = subset(stocksTest, clusterTest==1)
stocksTest2 = subset(stocksTest, clusterTest==2)
stocksTest3 = subset(stocksTest, clusterTest==3)
```
Logistic Regression Modeling on Specific Clusters
====================================================
```{r}
stocksModel1 = glm(PositiveDec ~ ., data=stocksTrain1, family=binomial)
summary(stocksModel1)
stocksModel2 = glm(PositiveDec ~ ., data=stocksTrain2, family=binomial)
summary(stocksModel2)
stocksModel3 = glm(PositiveDec ~ ., data=stocksTrain3, family=binomial)
summary(stocksModel3)
```
Predictions on the Test Set
======================================
```{r}
PredictTest1 = predict(stocksModel1, newdata=stocksTest1, type="response")
predtable = table(stocksTest1$PositiveDec, PredictTest1 >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
```{r}
PredictTest2 = predict(stocksModel2, newdata=stocksTest2, type="response")
predtable = table(stocksTest2$PositiveDec, PredictTest2 >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
```{r}
PredictTest3 = predict(stocksModel3, newdata=stocksTest3, type="response")
predtable = table(stocksTest3$PositiveDec, PredictTest3 >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
Measuring Overall Test-Set Accuracy
===========================================
```{r}
AllPredictions = c(PredictTest1, PredictTest2, PredictTest3)
AllOutcomes = c(stocksTest1$PositiveDec, stocksTest2$PositiveDec, stocksTest3$PositiveDec)
predtable = table(AllOutcomes, AllPredictions >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`