Unit 6 - Clustering: Lecture 1 - Netflix
================================================
Loading and Pre-Processing the Dataset
=================================
Add column names, remove variables we aren't using, and remove non-unique movies.
```{r}
movies = read.table("movieLens.txt", header=FALSE, sep="|", quote="\"")
colnames(movies) = c("ID", "Title", "ReleaseDate", "VideoReleaseDate", "IMDB", "Unknown", "Action", "Adventure", "Animation", "Childrens", "Comedy", "Crime", "Documentary", "Drama", "Fantasy", "FilmNoir", "Horror", "Musical", "Mystery", "Romance", "SciFi", "Thriller", "War", "Western")
movies$ID = NULL
movies$ReleaseDate = NULL
movies$VideoReleaseDate = NULL
movies$IMDB = NULL
movies = unique(movies)
str(movies)
```
Hierarchical Clustering
=================================
```{r}
distances = dist(movies[2:20], method="euclidean")
clusterMovies = hclust(distances, method="ward.D")
plot(clusterMovies)
```
Too many datapoints, so all of the x-axis is essentially black. These are overlapped labels.
```{r}
clusterGroups = cutree(clusterMovies, k = 10)
tapply(movies$Action, clusterGroups, mean)
```
This divides the movies into the clusters defined by clusterGroups and then gives the average rating for movies$Action for that cluster
```{r}
subset(movies, Title=="Men in Black (1997)")
clusterGroups[257]
cluster2 = subset(movies, clusterGroups == 2)
cluster2$Title[1:10]
```
Looking at a Specific Cluster Group
=============================================
```{r}
colMeans(subset(movies[2:20], clusterGroups == 1))
```
Using Split and lapply To Look at All Clusters
=================================================
```{r}
spl = split(movies[2:20], clusterGroups)
colMeans(spl[[1]])
lapply(spl, colMeans)