Unit 5 - Text Analytics : Assignment 3 - Spam
========================================================
Data Loading
========================================
```{r}
emails = read.csv("emails.csv", stringsAsFactors=FALSE)
str(emails)
which.min(nchar(emails$text))
```
Corpus Construction
==================================
```{r}
suppressWarnings(suppressMessages(library(tm)))
corpus = Corpus(VectorSource(emails$text))
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, removeWords, stopwords("english"))
corpus = tm_map(corpus, stemDocument)
```
Document Term Matrix
---------------------------------------
```{r}
dtm = DocumentTermMatrix(corpus)
spdtm = removeSparseTerms(dtm, 0.95)
```
Data Frame Construction
====================================
```{r}
emailsSparse = as.data.frame(as.matrix(spdtm))
colnames(emailsSparse) = make.names(colnames(emailsSparse))
which.max(colSums(emailsSparse))
emailsSparse$spam = emails$spam
emailsSparse$spam = as.factor(emailsSparse$spam)
```
Splitting the Data
====================================
```{r}
suppressWarnings(library(caTools))
set.seed(123)
spl = sample.split(emailsSparse$spam, SplitRatio=0.7)
train = subset(emailsSparse, spl == TRUE)
test = subset(emailsSparse, spl == FALSE)
```
Baseline Model
===============================
```{r}
basetable = table(test$spam)
```
**Accuracy:** `r max(c(basetable[1],basetable[2]))/(basetable[1]+basetable[2])`
Modeling on the Training Set
======================================================
Logistic Regression Model
================================================
```{r}
spamLog = glm(spam ~ ., data=train, family=binomial)
summary(spamLog)
```
Logistic Regression Predictions
-------------------------------------------
```{r}
pred = predict(spamLog, newdata=train, type="response")
predtable = table(train$spam, pred >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / nrow(train)`
Logistic Regression ROCR AUC
---------------------------
```{r}
suppressWarnings(suppressMessages(library(ROCR)))
predROCR = prediction(pred, train$spam)
performance(predROCR, "auc")@y.values
```
CART Model
==============================================
```{r}
suppressWarnings(library(rpart))
suppressWarnings(library(rpart.plot))
spamCART = rpart(spam ~ ., data=train, method="class")
prp(spamCART)
```
CART Predictions
------------------------------------------
```{r}
pred = predict(spamCART)
pred.prob = pred[,2]
predtable = table(train$spam, pred.prob >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / nrow(train)`
CART ROCR AUC
---------------------------
```{r}
predROCR = prediction(pred.prob, train$spam)
performance(predROCR, "auc")@y.values
```
Random Forest Model
====================================
```{r}
suppressWarnings(library(randomForest))
set.seed(123)
spamRF = randomForest(spam ~ ., data=train)
```
Random Forest Predictions
------------------------------
```{r}
pred = predict(spamRF, type="prob")[,2]
predtable = table(train$spam, pred >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / nrow(train)`
Random Forest ROCR AUC
---------------------------
```{r}
predROCR = prediction(pred, train$spam)
performance(predROCR, "auc")@y.values
```
Predictions on the Testing Set
=======================================
Logistic Regression Predictions on the Test Data
======================================
```{r}
pred = predict(spamLog, newdata=test, type="response")
predtable = table(test$spam, pred >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
Logistic Regression ROCR AUC
---------------------------
```{r}
predROCR = prediction(pred, test$spam)
performance(predROCR, "auc")@y.values
```
CART Predictions on the Test Data
=============================================
```{r}
pred = predict(spamCART, newdata=test)
pred.prob = pred[,2]
predtable = table(test$spam, pred.prob >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
CART ROCR AUC
---------------------------
```{r}
predROCR = prediction(pred.prob, test$spam)
performance(predROCR, "auc")@y.values
```
Random Forest Predictions on the Test Data
============================================
```{r}
pred = predict(spamRF, newdata=test, type="prob")[,2]
predtable = table(test$spam, pred >= 0.5)
predtable
```
**Accuracy:** `r (predtable[1,1] + predtable[2,2]) / sum(predtable)`
Random Forest ROCR AUC
---------------------------
```{r}
predROCR = prediction(pred, test$spam)
performance(predROCR, "auc")@y.values
```