Unit 7 - Visualizations: Assignment 1: Election Forecasting Revisited
=============================================================
Data Load and Pre-Process
-----------------------------------
```{r}
library(ggplot2)
library(maps)
library(ggmap)
statesMap = map_data("state")
str(statesMap)
```
Map Plotting
----------------------------
```{r}
ggplot(statesMap, aes(x=long, y=lat, group=group)) + geom_polygon(fill="white", color="black")
polling = read.csv("PollingImputed.csv")
str(polling)
```
Splitting the Data
------------------------
```{r}
Train = subset(polling, Year <= 2008)
Test = subset(polling, Year == 2012)
dim(Train)
dim(Test)
```
Logistic Regression Model
-------------------------
```{r}
mod2 = glm(Republican ~ SurveyUSA + DiffCount, data=Train, family="binomial")
TestPrediction = predict(mod2, newdata=Test, type="response")
TestPredictionBinary = as.numeric(TestPrediction > 0.5)
predictionDataFrame = data.frame(TestPrediction, TestPredictionBinary, Test$State)
predtable = table(Test$Republican, TestPredictionBinary)
predtable
```
**Accuracy:** `r (predtable[1,1]+predtable[2,2])/sum(predtable)`

Merging the Model DataSet with the Map
=============================================
```{r}
predictionDataFrame$region = tolower(predictionDataFrame$Test.State)
predictionMap = merge(statesMap, predictionDataFrame, by="region")
predictionMap = predictionMap[order(predictionMap$order),]
ggplot(predictionMap, aes(x=long, y=lat, group=group, fill=TestPredictionBinary)) +
      geom_polygon(color="black")
```

Let's make sure that the legend only has two discrete outcomes
```{r}
ggplot(predictionMap, aes(x=long, y=lat, group=group, fill=TestPredictionBinary)) +
      geom_polygon(color = "black") + 
      scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), 
                          labels = c("Democrat", "Republican"), name = "Prediction 2012")
```
Alternatively we could plot the probabilities associated with the prediction for each state
```{r}
ggplot(predictionMap, aes(x=long, y=lat, group=group, fill=TestPrediction)) +
      geom_polygon(color = "black") + 
      scale_fill_gradient(low = "grey", high = "black", guide = "legend", breaks= c(0,1), 
                          labels = c("Democrat", "Republican"), name = "Prediction 2012")
```
Experimenting with different parameters
```{r}
ggplot(predictionMap, aes(x=long, y=lat, group=group, fill=TestPredictionBinary)) +
      geom_polygon(color = "black", linetype=3) + 
      scale_fill_gradient(low = "blue", high = "red", guide = "legend", breaks= c(0,1), 
                          labels = c("Democrat", "Republican"), name = "Prediction 2012")