Unit 7 - Visualizations : Lecture 1 - WHO
=============================================
Data Loading and Pre-Processing
------------------------------------
```{r}
WHO = read.csv("WHO.csv")
str(WHO)
```
Plotting
================
```{r}
plot(WHO$GNI, WHO$FertilityRate)
```
GGPlot2 Plotting
--------------------------
```{r}
suppressWarnings(library(ggplot2))
scatterplot = ggplot(WHO, aes(x = GNI, y=FertilityRate))
scatterplot + geom_point()
scatterplot + geom_line()
scatterplot + geom_point(color="blue", size=3, shape=17)
fertilityGNIplot = scatterplot + geom_point(color="darkred", size=3, shape=15) + ggtitle("Fertility Rate vs. Gross National Income")
fertilityGNIplot
```
Save our file
===========================
```{r}
pdf("MyPlot.pdf")
print(fertilityGNIplot)
dev.off()
```
Color our Points by Other Variables
===============================
```{r}
ggplot(WHO, aes(x = GNI, y = FertilityRate, color=Region)) + geom_point() + ggtitle("Colored by Region (Categorical Variable)")
ggplot(WHO, aes(x = GNI, y = FertilityRate, color=LifeExpectancy)) + geom_point() + ggtitle("Colored by Life Expectancy (Continuous Variable)")
```
Log Plotting
-----------------
```{r}
ggplot(WHO, aes(x = FertilityRate, y = Under15)) + geom_point()
```
This looks like there is a log model.
```{r}
ggplot(WHO, aes(x = log(FertilityRate), y = Under15)) + geom_point()
model = lm(Under15 ~ log(FertilityRate), data=WHO)
summary(model)
```
Looks like the model fits very well. We may not have noticed that this would occur without the visualization.
Adding the new fit line
====================================
```{r}
ggplot(WHO, aes(x = log(FertilityRate), y = Under15)) + geom_point() + stat_smooth(method="lm", level=0.99)
ggplot(WHO, aes(x = log(FertilityRate), y = Under15)) + geom_point() + stat_smooth(method="lm", se=FALSE, color="orange")
```
Pallete Adjustment
======================
```{r}
ggplot(WHO, aes(x = FertilityRate, y = Under15, color=Region)) + geom_point() + scale_color_brewer(palette="Dark2")
