Unit 7 - Visualizations : Lecture 2 - Predictive Policing
============================================================
Loading and Pre-Processing
-----------------------------------
```{r}
mvt = read.csv("mvt.csv", stringsAsFactors=FALSE)
str(mvt)
mvt$Date = strptime(mvt$Date, format="%m/%d/%y %H:%M")
mvt$Weekday = weekdays(mvt$Date)
mvt$Hour = mvt$Date$hour
str(mvt)
```
Exploratory Analysis
======================================
```{r}
table(mvt$Weekday)
WeekdayCounts = as.data.frame(table(mvt$Weekday))
str(WeekdayCounts)
suppressWarnings(library(ggplot2))
ggplot(WeekdayCounts, aes(x=Var1, y=Freq)) + geom_line(aes(group=1))
```

Looks like ggplot put the days of the week in alphabetical order. We'd like them in chronological order.
```{r}
WeekdayCounts$Var1 = factor(WeekdayCounts$Var1, ordered=TRUE, levels=c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
ggplot(WeekdayCounts, aes(x=Var1, y=Freq)) + geom_line(aes(group=1)) + xlab("Day of the Week") + ylab("Total Motor Vehicle Thefts")
```
Adding Dotted Lines
------------------------------
```{r}
ggplot(WeekdayCounts, aes(x=Var1, y=Freq)) + geom_line(aes(group=1), linetype=2) + xlab("Day of the Week") + ylab("Total Motor Vehicle Thefts")
```
Changing the Lightness of the lines
--------------------------------------
```{r}
ggplot(WeekdayCounts, aes(x=Var1, y=Freq)) + geom_line(aes(group=1), alpha=0.3) + xlab("Day of the Week") + ylab("Total Motor Vehicle Thefts")
```
Adding Day of the Week
--------------------------------
```{r}
table(mvt$Weekday, mvt$Hour)
DayHourCounts = as.data.frame(table(mvt$Weekday, mvt$Hour))
str(DayHourCounts)
DayHourCounts$Hour = as.numeric(as.character(DayHourCounts$Var2)) #Converts factor variable to a numeric variable
ggplot(DayHourCounts, aes(x=Hour, y=Freq)) + geom_line(aes(group=Var1))
```

Let's add colors so that we can differentiate between the days of the week
```{r}
ggplot(DayHourCounts, aes(x=Hour, y=Freq)) + geom_line(aes(group=Var1, color=Var1, size=2))
```
Creating a Heatmap
=================================
```{r}
DayHourCounts$Var1 = factor(DayHourCounts$Var1, ordered=TRUE, levels=c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
ggplot(DayHourCounts, aes(x=Hour,y=Var1)) + geom_tile(aes(fill=Freq))
```

Some Further Changes
-------------------------
```{r}
ggplot(DayHourCounts, aes(x=Hour,y=Var1)) + geom_tile(aes(fill=Freq)) + scale_fill_gradient(name="Total MV Thefts") + theme(axis.title.y = element_blank())
ggplot(DayHourCounts, aes(x=Hour,y=Var1)) + geom_tile(aes(fill=Freq)) + scale_fill_gradient(name="Total MV Thefts", low="white", high="red") + theme(axis.title.y = element_blank())
```
Applying a Heatmap to a Geographic Map
===============================
```{r}
suppressWarnings(library(maps))
suppressWarnings(library(ggmap))
chicago = get_map(location="chicago", zoom=11)
ggmap(chicago)
ggmap(chicago) + geom_point(data=mvt[1:100,], aes(x=Longitude, y=Latitude))
```
Building the Densities
---------------------------------
```{r}
LatLonCounts = as.data.frame(table(round(mvt$Longitude, 2), round(mvt$Latitude,2)))
str(LatLonCounts)
LatLonCounts$Long = as.numeric(as.character(LatLonCounts$Var1)) #Convert Factor to Numeric
LatLonCounts$Lat = as.numeric(as.character(LatLonCounts$Var2)) #Convert Factor to Numeric
ggmap(chicago) + geom_point(data=LatLonCounts, aes(x = Long, y = Lat, color=Freq, size=Freq))
```

Changing the color scheme
```{r}
ggmap(chicago) + geom_point(data=LatLonCounts, aes(x = Long, y = Lat, color=Freq, size=Freq)) + scale_color_gradient(low="yellow", high="red")
```
Using geom_tile to Make a Continuous HeatMap
=======================
```{r}
ggmap(chicago) + geom_tile(data=LatLonCounts, aes(x=Long, y= Lat, alpha=Freq), fill="red")
```
Removing Tiles where Freq==0
================================
```{r}
LatLonCounts2 = subset(LatLonCounts, Freq > 0)
ggmap(chicago) + geom_tile(data=LatLonCounts2, aes(x=Long, y= Lat, alpha=Freq), fill="red")
```
We Removed `r nrow(LatLonCounts) - nrow(LatLonCounts2)` observations from the dataset.
United States Murder Visualization
========================================
```{r}
murders = read.csv("murders.csv")
str(murders)
statesMap = map_data("state")
str(statesMap)
ggplot(statesMap, aes(x=long,y=lat,group=group)) + geom_polygon(fill="white", color="black")
murders$region = tolower(murders$State)
```
Merge Function
======================
The Merge function joins rows of a dataframe on a shared variable
```{r}
murderMap = merge(statesMap, murders, by="region")
str(murderMap)
```
Plotting our Newly Joined Data
---------------------------------
```{r}
ggplot(murderMap, aes(x=long, y=lat, group=group, fill=Murders)) + geom_polygon(color="black") + scale_fill_gradient(low="black", high="red", guide="legend")
```

California and Texas seem to be emphasized, but we have not normalized on population. Let's look at state Populations. Should look very similiar
```{r}
ggplot(murderMap, aes(x=long, y=lat, group=group, fill=Population)) + geom_polygon(color="black") + scale_fill_gradient(low="black", high="red", guide="legend")
```
Adding a Murder Rate Variable
-------------------------------
```{r}
murderMap$MurderRate = murderMap$Murders/murderMap$Population*100000
ggplot(murderMap, aes(x=long, y=lat, group=group, fill=MurderRate)) + geom_polygon(color="black") + scale_fill_gradient(low="black", high="red", guide="legend")
```
Removing Outliers
-------------------------
```{r}
ggplot(murderMap, aes(x=long, y=lat, group=group, fill=MurderRate)) + geom_polygon(color="black") + scale_fill_gradient(low="black", high="red", guide="legend", limits=c(0,10))
```
Gun Ownership
--------------------------------
```{r}
ggplot(murderMap, aes(x=long, y=lat, group=group, fill=GunOwnership)) + geom_polygon(color="black") + scale_fill_gradient(low="black", high="red", guide="legend")
mean(subset(murderMap, region=="california")$GunOwnership)
mean(subset(murderMap, region=="montana")$GunOwnership)
mean(subset(murderMap, region=="texas")$GunOwnership)
mean(subset(murderMap, region=="louisiana")$GunOwnership)
mean(subset(murderMap, region=="missouri")$GunOwnership)
```
